The Distributed Nature of Copycat..? (WIP)

### 2017-11-13 papers/paper.tex
Fixes some silly wording in paper

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Distributed Parallel Terraced Scan}
%% \title{The Brain as a Distributed System}?
\author{Lucas Saldyt, Alexandre Linhares}

@@

\section{Normal Science}

\section{Notes}

    According to the differences we can enumerate between brains and computers, it is clear that, since computers are universal and have vastly improved in the past five decades, that computers are capable of simulating intelligent processes. 
    [Cite Von Neumann]. 
    Primarily, the main obstacle now lies in our comprehension of intelligent processes. 
    Once we truly understand the brain, writing software that emulates intelligence will be a relatively simple software engineering task. 
    However, we must be careful to remain true to what we already know about intelligent processes so that we may come closer to learning more about them and eventually replicating them in full. 
    The largest difference between the computer and the brain is the distributed nature of computation. 
    Specifically, our computers as they exist today have central processing units, where literally all of computation happens. 
    On the other hand, our brains have no central location where all processing happens. 
    Luckily, the speed advantage and universality of computers makes it possible to simulate the distributed behavior of the brain. 
    However, this simulation is only possible if computers are programmed with concern for the distributed nature of the brain.
    [Actually, I go back and forth on this: global variables might be plausible, but likely aren't]
    Also, even though the brain is distributed, some clustered processes must take place.
    So, centralized structures should be removed from the copycat software, because they will likely improve the accuracy of simulating intelligent processes.
    It isn't clear to what degree this refactor should take place.
    The easiest target is the central variable, temperature, but other central structures exist.
    This paper focuses primarily on temperature, and the unwanted global unification associated with it.

@@

    However, I question the assumption that the human brain has absolutely no centralized processing.
    For example, input and output chanels (i.e. speech mechanisms) are not accessible from the entire brain.
    Also, brain-region science leads me to believe that some (for example, research concerning wernicke's or broca's areas) brain regions truly are "specialized," and thus lend some support to the existence of centralized structures in a computer model of the brain.
    However, these centralized structures may be emergent?

@@

    Another important problem is defining the word "effective".
    I suppose that "effective" would mean capable of solving problems effectively.
    However, it isn't clear to me that removing temperature increases the ability to solve problems effectively.
    Is this because models are aloud to have centralized structures, or because temperature isn't the only centralized structure?

@@

@@

>>>>

%% Useful packages
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\definecolor{lightgrey}{rgb}{0.9, 0.9, 0.9}
\lstset{ %
    backgroundcolor=\color{lightgrey}}

\title{The Distributed Nature of Copycat..? (WIP)}
\author{Lucas Saldyt, Alexandre Linhares}

@@

\subsection{Notes}

    According to the differences we can enumerate between brains and computers, it is clear that, since computers are universal and have vastly improved in the past five decades, that computers are capable of simulating intelligent processes. 
    [Cite Von Neumann]. 
    Primarily, the main obstacle now lies in our comprehension of intelligent processes. 
    Once we truly understand the brain, writing software that emulates intelligence will be a relatively simple software engineering task. 
    However, we must be careful to remain true to what we already know about intelligent processes so that we may come closer to learning more about them and eventually replicating them in full. 
    The largest difference between the computer and the brain is the distributed nature of computation. 
    Specifically, our computers as they exist today have central processing units, where literally all of computation happens. 
    On the other hand, our brains have no central location where all processing happens. 
    Luckily, the speed advantage and universality of computers makes it possible to simulate the distributed behavior of the brain. 
    However, this simulation is only possible if computers are programmed with concern for the distributed nature of the brain.
    [Actually, I go back and forth on this: global variables might be plausible, but likely aren't]
    Also, even though the brain is distributed, some clustered processes must take place.
    In general, centralized structures should be removed from the copycat software, because they will likely improve the accuracy of simulating intelligent processes.
    It isn't clear to what degree this refactor should take place.
    The easiest target is the central variable, temperature, but other central structures exist.
    This paper focuses primarily on temperature, and the unwanted global unification associated with it.

@@

    However, I question the assumption that the human brain has absolutely no centralized processing.
    For example, input and output channels (i.e. speech mechanisms) are not accessible from the entire brain.
    Also, brain-region science leads me to believe that some (for example, research concerning wernicke's or broca's areas) brain regions truly are "specialized," and thus lend some support to the existence of centralized structures in a computer model of the brain.
    However, these centralized structures may be emergent?

@@

    Another important problem is defining the word "effective".
    I suppose that "effective" would mean capable of solving fluid analogy problems, producing similar answers to an identically biased human.
    However, it isn't clear to me that removing temperature increases the ability to solve problems effectively.
    Is this because models are aloud to have centralized structures, or because temperature isn't the only centralized structure?

@@

\subsection{Initial Formula Adjustments}

This research begin with adjustments to probability weighting formulas.

In copycat, temperature affects the simulation in multiple ways:

\begin{enumerate}
    \item Certain codelets are probabalistically chosen to run
    \item Certain structures are probabalistically chosen to be destroyed
    \item ...
\end{enumerate}

In many cases, the formulas "get-adjusted-probability" and "get-adjusted-value" are used.
Each curves a probability as a function of temperature.
The desired behavior is as follows:
At high temperatures, the system should explore options that would otherwise be unlikely.
So, at temperatures above half of the maximum temperature, probabilities with a base value less than fifty percent will be curved higher, to some threshold.
At temperatures below half of the maximum temperature, probabilities with a base value above fifty percent will be curved lower, to some threshold.

The original formulas being used to do this were overly complicated.
In summary, many formulas were tested in a spreadsheet, and an optimal one was chosen that replicated the desired behavior.
[]

\lstinputlisting[language=Python]{test.py}

@@

\end{verbatim}
